Characterizing Optimizations to Memory Access Patterns using Architecture-Independent Program Features

### 2020-01-20 paper/paper.tex
fix intro

	The structure of this paper is as follows.
	In section~\ref{motivating example} we use the example of matrix multiplication on a GPU to showcase the specific vendor-recommended optimizations our work aims to measure.
	In section~\ref{related work} we discuss how AIWC and its precursors profiled memory access patterns in an architecture-independent fashion and also consider relevant architecture-dependent approaches to memory access profiling.
	In section \ref{method} we consider non-parallel memory metrics collected by AIWC and evaluate the suitability of these metrics for capturing the impact of performance optimizations to various OpenCL codes.
	In section~\ref{discussion} we propose a new parallel spatial locality metric and implement it in the AIWC framework.
	In section~\ref{results} we present the collected metric for selected benchmarks from the Extended OpenDwarfs benchmark suite to validate our methodology in this paper.
	Finally, in section~\ref{future work} we discuss further avenues to extend our work and conclude.

>>>>

	The structure of this paper is as follows.
	In section~\ref{motivating example} we use the example of matrix multiplication on a GPU to showcase the specific vendor-recommended optimizations our work aims to measure.
	In section~\ref{related work} we discuss how AIWC and its precursors profiled memory access patterns in an architecture-independent fashion and also consider relevant architecture-dependent approaches to memory access profiling.
	In section \ref{method} we consider non-parallel memory metrics collected by AIWC and evaluate the suitability of these metrics for capturing the impact of performance optimizations to various OpenCL codes.
	In section~\ref{discussion} we propose a new parallel spatial locality metric, implement it in the AIWC framework, and evaluate it over the matrix multiplication example from section~\ref{motivating example}.
	In section~\ref{results} we present the collected metric for selected benchmarks from the Extended OpenDwarfs benchmark suite to validate our methodology in this paper.
	Finally, in section~\ref{future work} we discuss further avenues to extend our work and conclude.
